\textbf{Supplementary Materials}\\ A Critical Appraisal of the Zero-Multiple Method: Structural, Thermodynamic, Dielectric, and Dynamical Properties of a Water System

### 2014-11-08 writedown/zm/paper.water/si.tex
add SI and gp files.

%2multibyte Version: 5.50.0.2952 CodePage: 932
% \documentclass[reprint,unsortedadress,oneclumn]{revtex4-1}
%\documentclass[aip,jcp,a4paper,preprint,unsortedaddress,onecolumn,fleqn]{revtex4-1}

\documentclass[a4paper,preprint,unsortedaddress,onecolumn,fleqn]{revtex4}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{amsmath,amssymb,amsfonts,latexsym}
\usepackage[dvips]{graphicx}
\usepackage{color}
\usepackage{indentfirst}
\usepackage{rotating,booktabs}

@@

\title{A Critical Appraisal of the Zero-Multiple Method: Structural,
Thermodynamic, Dielectric, and Dynamical Properties of a Water System}
\author{Han Wang}
\email{han.wang@fu-berlin.de}
\author{Ikuo Fukuda}
\email{ifukuda@protein.osaka-u.ac.jp}

@@

\section{Introduction}

A very short overview of the existing electrostatic interaction methods. Two
classes in general: Long-range treatment, e.g.~Ewald and derived methods
like SPME. Short-range treatment, like RF and ZM.

The importance of developing a short-range method for the electrostatic
interaction.

Zero-Multiple method, an overview, achievements, successful applications.

The purpose of this work: Extensive and strict tests investigating the
reliability of Zero-Multiple method in water simulation, which is the most
important solvent.

The structure of the paper.

[{\color{blue} COMMENT: I can contribute this section later}]

\section{Zero-Multipole Summation}

Introduction of the ZM method, formula...[ {\color{blue} COMMENT: I can
write here later}]

{\color{red} If we want to discuss the issue of cut-off method, a short
introduction of the group cut-off v.s.~the atom cut-off method. (will
discuss the implementation in gromacs later) }[ {\color{blue} COMMENT: what
do you mean? \recheck{I mean the explanation of group and atomistic cut-off method. the traditional gromacs uses gropu cut-off as default. We need instead the atomistic cut-off}}]

\section{Material and Methods}

\subsection{Benchmark quantities}

In order to investigate the performance of ZM method, we simulate the water
system by using both SPME and ZM methods, and evaluate a set of \emph{%
benchmark quantities}. This set covers a broad range of water properties
that are of general interest. It includes the structure property (radial
distribution function), the thermodynamic properties (pressure, excess
chemical potential, constant volume/pressure heat capacity, isothermal
compressibility, thermal expansion coefficient), dielectric properties
(dielectric constant and Kirkwood-G factor) and dynamical properties
(diffusion constant and viscosity). The definitions and computing methods of
these quantities are provided in details in Appendix.~\ref%
{appendix:benchmark}. By comparing ZM to SPME, a good consistency in
computing the benchmark quantities would indicate a good accuracy of the ZM
method. More importantly, the benchmark tests provide knowledge in the
situations when the ZM method does not work so well, and help in finding the
way of tuning the working parameters to achieve higher accuracy. The ZM
method is also compared to the traditional short-range method: RF.

\subsection{Simulation protocols}
\label{sec:protocols}
In this work, we focus on a system of water molecules modeled
by TIP3P~\cite{jorgensen1983comparison} point-charge particles. 
% Other point-charge water models differ in the modeling parameters, and
The accuracy of ZM method in other water models is out of the scope of the
current work. However, since the point-charge water models share similar
idea, and only differ in the model parameters, it is highly probable that ZM
works well with other water models if it works well with TIP3P.

All simulations were performed by Gromacs~4.6.5~\cite{hess2008gromacs,
pronk2013gromacs} complied by GNU C compiler with single-precision floating
point. The size of the systems and corresponding number of molecules used
for MD simulations are summarized in Tab.~\ref{tab:tmp1}. The benchmark
quantities were calculated in either canonical (NVT) or isothermal-isobaric
(NPT) ensemble, with equilibrium temperature $T=300$~K. In order to simulate
at the desired temperature, the systems $S_{1}$ and $S_{1}^{\prime }$ were
coupled to Nos\'{e}-Hoover~\cite{nose1984molecular,hoover1985canonical}
thermostat with time-scale $\tau _{T}=1.0$~ps, while systems $M_{1}$, $%
M_{1}^{\prime }$, $L_{0}$, $L_{1}$ and $L_{1}^{\prime }$ were coupled to
Langevin thermostat with time-scale $\tau _{T}=0.1$~ps. In the NPT
simulations, the systems were further coupled to the Parrinello-Rahman
barostat~\cite{parrinello1980crystal,parrinello1981polymorphic} (in Gromacs
implementation) with time-scale $\tau _{P}=0.5$~ps to equilibrate the system
at 1~Bar. All systems were integrated with leap-frog scheme at a time-step
of 0.001~ps.

The neighbor lists were updated every 5 time-steps. The \textquotedblleft 
\texttt{group}\textquotedblright\ cut-off scheme in Gromacs was used. In
order to mimic the atomistic cut-off manner, the radius for neighbor list
building was set 0.3~nm larger than the cut-off radius (the maximum of
Coulomb cut-off and the van der Waals cut-off). [ {\color{blue} COMMENT:
Yes,..., this is not easy to understand how we mimic AC. \recheck{it should be OK as it is now.}}] To make sure the
van der Waals interactions were cut-off in a smooth way, they are modified
in a shell of $0.05$~nm width near the cut-off sphere by the Gromacs
\textquotedblleft \texttt{shift}\textquotedblright\ method.

The short-range part of SPME method \recheck{was cut-offed at 1.9~nm, and was} smoothed in a shell of $0.05$~nm
width by the Gromacs \textquotedblleft \texttt{pme-switch}%
\textquotedblright\ method. The reciprocal space grid spacing was set to
0.06~nm, with B-Spline interpolation order of 6. These parameters were
chosen to be more accurate than the Gromacs default choices (grid spacing
0.12~nm and interpolation order 4). The splitting parameter was optimized by
the error estimate for the SPME method, which is implemented in Gromacs by
tool \textquotedblleft \texttt{g\_pme\_error}\textquotedblright ~\cite%
{wang2010optimizing}. The optimized real space and reciprocal space force
computing errors were equally distributed as $1.4\times 10^{-4}$~kJ/(mol
nm). Since the magnitude of the forces are of order $10^{2}$~kJ/(mol nm),
this force computing precision almost reaches the limit of the
single-precision representation of the floating point numbers.

In the simulations of the RF method, the interactions were cut-off in the
group manner, so the radius for neighbor list building is set identical to
the cut-off radius. No cut-off smoothing of the electrostatic interaction
was applied in the cases of RF simulations. We used $1.2$~nm
cut-off and the experimental dielectric constant $\varepsilon _{\textrm{rf}}=80$.

The ZM method was implemented in Gromacs with the tabulated electrostatic
interaction. A home-made code was used to generate the interaction tables.

\begin{table}[tbp]
\caption{A list of systems simulated in this work. We report, from left to
right, the number of water molecules in the system (TIP3P model),
equilibrium box size, length of equilibriation, length of productive
trajectory. }
\label{tab:tmp1}\centering
\vskip .5cm 
\begin{tabular*}{0.5\textwidth}{@{\extracolsep{\fill}}crrrr}
\hline\hline
System & $N$ & $V$ [$\text{nm}^3$] & $T_{\text{eq}}$ [ps] & $T_{\text{prod}}$
[ps] \\ \hline
$S^{\prime }_1$ & 2,500 & $4.24^3$ & -- & 6,000 \\ 
$S_1$ & 2,500 & $4.24^3$ & 3,000 & 27,000 \\ \hline
$M^{\prime }_1$ & 4,500 & $5.15^3$ & -- & 6,000 \\ 
$M_1$ & 4,500 & $5.15^3$ & 3,000 & 17,000 \\ \hline
$L_0$ & 13,824 & $7.49^3$ & 200 & 1,800 \\ 
$L^{\prime }_1$ & 13,824 & $7.49^3$ & -- & 10,000 \\ 
$L_1$ & 13,824 & $7.49^3$ & 3,000 & 17,000 \\ \hline\hline
\end{tabular*}%
\end{table}

The initial configurations were prepared by in the following steps: (1) An
NPT simulation of system $L_{0}$ with SPME electrostatic was performed. The
equilibrium density (984.1~$\text{kg}/\text{m}^{3}$) of the system is
calculated from this simulation. (2) Initial configurations that contains
2500, 4500 and 13824 molecules were generated at the calculated equilibrium
density. (3) NVT simulations with SPME electrostatic for system $%
S_{1}^{\prime }$, $M_{1}^{\prime }$ and $L_{1}^{\prime }$ are performed. (4)
The final configurations of $S_{1}^{\prime }$ and $M_{1}^{\prime }$
were used as initial configurations for system $S_{1}$ and $M_{1}$,
respectively. The final configuration of $L_{1}^{\prime }$ was
used as initial configurations for system $L_{0}$ and $L_{1}$. % The SPME
% parameters for all simulations reported by this work is: real space
% cut-off 1.90~nm.
% [ {\color{blue} COMMENT: The following has been moved here, OK? If we need a
%   special care, please modify.}]
Using the density in the NVT simulation with
SPME electrostatic, the pressure ($-0.4\pm 1.5$~Bar) is reproducing the
target pressure of 1.0~Bar, which means the system is in desired
thermodynamic state.

% The cut-off is smoothed from 1.85 to 1.90~nm by the
% ``\texttt{switch}'' method provide by Gromacs
% 4.6~\cite{hess2008gromacs, pronk2013gromacs}.

The smallest system $S_{1}$ was adopted for the quantities that are computed
by estimating fluctuations (in this work heat capacities, compressibility,
thermal expansion coefficient, dielectric constant, diffusion constant and
viscosity are fluctuations. See details in Appendix~\ref{appendix:benchmark}%
), because simply increasing the size of the system does not
improve the accuracy of the simulation~\cite%
{milchev1986fluctuations,ferrenberg1991statistical}. The optimal way of
measuring these properties is to simulate with smaller systems 
% (as far as the finite size effect is negligible)
and run longer simulations for longer time-averages. The reason of using Nos%
\'{e}-Hoover thermostat is that it perturbs the dynamics of the system only
slightly, while the Langevin thermostat is likely to substantially change
the dynamics when the coupling is very strong, therefore, the former was
used in computing the dynamical properties like the diffusion constant and
viscosity. The quantities that are ensemble averages (in this work,
pressure, chemical potential, radial distribution function and Kirkwood-G
factor are of this type) were computed by the largest system $L_{0}$ or $L_{1}$, in order to
achieve higher parallel efficiency. The system $M_{1}$ is simulated to
investigate the size-dependency of the Kirkwood-G factor~\cite%
{vanderSpoel2006origin}.

\section{Results and discussions}

In this section we compare the benchmark quantities of the ZM method to the
SPME method to investigate the accuracy of the former. The comparison to the
RF method will also be mentioned, to show that the ZM is a promising
replacement of the RF method.

\subsection{Thermodynamic properties}

\begin{sidewaystable}
  \centering
  \caption{The excess chemical potential $\mu^\exc$, constant volume molar heat capacity $C_{v,m}$, dielectric constant $\eps$, diffusion constant $D$, viscosity $\eta$, constant pressure molar heat capacity $C_{v,m}$, isothermal compressibility $\kappa_T$ and
    thermal expansion coefficient $\alpha_V$
    calculated by different methods.    
    The parentheses in the last column show the statistical uncertainty
    at the confidence level of 95~\%.
    The bold numbers indicating that its deviation from the SPME result is larger than the statistical uncertainty.
  }
  \bigskip
  \centering\small\setlength\tabcolsep{2pt}
  \begin{tabular*}{0.99\textwidth}{@{\extracolsep{\fill}}cccc cccccccc}\hline\hline
    Method      &   $r_c$ &    $l$ & $\alpha$  & $\mu^\exc$  &$C_{v,m}$ & $C_{p,m}$ &   $\kappa_T$  &$\alpha_V$ &  $\eps$ & $D$ &  $\eta$  \\
                & [nm] & & [$\textrm{nm}^{-1}$] &   [kJ/mol] &[J/(mol K)] & [J/(mol K)] & [$10^{-10}\textrm{m}^2/\textrm{N}$] &  [$10^{-3}\textrm{K}^{-1}$]&  & [$10^{-9}\textrm{m}^2/\textrm{s}$] &  [$10^{-3}\textrm{Pa}\cdot\textrm{s}$]  \\
                &    &    &    &NVT $\systemla$&NVT $\systemsb$&  NPT $\systemsb$          &  NPT $\systemsb$    &  NPT $\systemsb$    & NVT $\systemsb$& NVT $\systemsb$    & NVT $\systemsb$       \\\hline
    SPME        &1.9 & -- &2.1 & $-26.1$ (0.2) & 72.2 (1.0)  &79.2 (0.9)           & 5.94 (0.05)               &1.03 (0.02)          & 98 (3)          &         5.86  (0.07)&         0.315  (0.007)\\
    RF          &1.2 & -- &--  & $-26.0$ (0.3) & 72.3 (0.8)  &\textbf{82.3} (1.0)  & \textbf{6.51} (0.06)      &\textbf{1.15} (0.02) & \textbf{59} (1) & \textbf{6.27} (0.19)& \textbf{0.449} (0.020)\\\hline
    ZM          &1.2 & 1  &0.0 & $-26.2$ (0.3) & 71.8 (0.9)  &78.9 (1.0)           & 5.87 (0.05)               &1.01 (0.02)          & 96 (2)          & \textbf{5.53} (0.11)& \textbf{0.346} (0.006)\\ 
    ZM          &1.2 & 1  &0.5 & $-26.4$ (0.3) & 72.3 (0.8)  &78.9 (0.9)           & 5.92 (0.05)               &\textbf{1.00} (0.02) & 97 (2)          & \textbf{5.52} (0.25)& \textbf{0.339} (0.008)\\ 
    ZM          &1.2 & 1  &1.0 & $-26.0$ (0.2) & 72.4 (0.8)  &78.4 (0.9)           & 5.95 (0.05)               &1.01 (0.02)          & 96 (2)          &        {5.78} (0.25)& \textbf{0.330} (0.011)\\ 
    ZM          &1.2 & 1  &1.5 & $-26.0$ (0.2) & 71.3 (0.8)  &80.2 (0.9)           & 5.97 (0.05)               &1.04 (0.02)          & 99 (3)          & \textbf{5.71} (0.09)&        {0.312} (0.008)\\ 
    ZM          &1.2 & 1  &2.0 & $-26.1$ (0.3) & 71.3 (0.8)  &79.4 (0.9)           & \textbf{6.05} (0.05)      &1.05 (0.02)          & 96 (3)          &        {5.90} (0.04)&        {0.307} (0.007)\\\hline
    ZM          &1.2 & 2  &0.0 & $-26.2$ (0.2) & 71.5 (0.9)  &79.7 (1.0)           & 5.95 (0.05)               &1.03 (0.02)          & 95 (3)          &         5.82  (0.27)&         0.318  (0.012)\\
    ZM          &1.2 & 3  &0.0 & $-26.2$ (0.2) & 71.6 (0.9)  &79.5 (1.0)           & 5.99 (0.05)               &1.02 (0.02)          & 96 (3)          &         5.79  (0.09)&         0.321  (0.008)\\
    ZM          &1.2 & 4  &0.0 & $-26.0$ (0.3) & 71.1 (0.8)  &79.5 (1.0)           & 5.96 (0.05)               &1.03 (0.02)          &100 (2)          &         5.89  (0.09)&         0.318  (0.013)\\
    \hline\hline
  \end{tabular*}
  \label{tab:thermo}
\end{sidewaystable}

Thermodynamic quantities including, the chemical potential, constant
volume/pressure molar heat capacity, isothermal compressibility and heat
expansion coefficient, are compared in Tab.~\ref{tab:thermo}. The ZM results
are in good consistency with the SPME results. In almost all cases the
deviations from the SPME results are smaller than the statistical
uncertainty. The RF was not so bad, but the results of the constant pressure
molar heat capacity and the isothermal compressibility show considerable
errors.
The dependence of the ZM results on the order\ $l$\ is \recheck{little}.
Although the splitting parameter, $\alpha $, also does not have significant
influence on almost all these thermodynamic quantities for $l=1$, only the
isothermal compressibility admits a weak dependence [\recheck{all except $\alpha=2$ are in the statistical uncertainty, by which we cannot say $\alpha=1$ is optimal... I remove ``and $\alpha=1$ seems optimal''}].
Overall, the ZM\ agrees with the SPME results without any bias and
out-performs the RF.

\recheck{
  It should be noticed that in the calculation of the chemical potential,
  the energy correction plays an important role. In the case of $l=1$, $\alpha = 0.0\,\text{nm}^{-1}$,
  it contributes $-0.1$~kJ/mol to the final result.
  By increasing $l$ or $\alpha$, this contribution
  becomes more significant, and reaches $-0.6$~kJ/mol for $l=4$, $\alpha = 0.0\,\text{nm}^{-1}$, and
  $-1.0$~kJ/mol for $l=1$, $\alpha = 2.0\,\text{nm}^{-1}$, respectively.
}

\begin{figure}[tbp]
\centering
\includegraphics[]{fig/nvt.pressure.1/pressure-methods.eps}
\caption{The pressure convergence with respect to the cut-off radius. The ZM
methods with order from 1 to 4 are compared with the RF. The splitting
parameter of ZM method is set to be $\protect\alpha =0.00\,\text{nm}^{-1}$.
The black solid line indicates the magnitude of the correct pressure: 1~Bar.
The error bars present the statistical uncertainty at 95\% confidence level.
\recheck{This uncertainty is twice of the standard deviation of the estimates (which are averages along MD trajectories) that
is calculated by the block average method~\cite{janke2002statistical}.}
}
\label{fig:pres-comp}
\end{figure}

We investigated the dependence on the cut-off radius, $r_{\text{c}}$, on the
pressure, simulated with system $L_{0}$. The pressure calculated by ZM
method of order $l=1,2,3$ and $4$ with $\alpha =0$ \ and that by the RF
method are plotted in Fig.~\ref{fig:pres-comp}. All ZM methods converges to
the target pressure at large enough cut-off radius. Lower order ZM presents
an smaller error in the pressure calculation than the higher order ZM
method. Note ZM $l=1$ tends to under-estimate the pressure, while ZM $l=2,3$
and 4 tends to over-estimate. However, the accuracy of ZM in pressure
calculation is much higher than that of the RF method.

\begin{figure}[tbp]
\centering
\includegraphics[width=0.5\textwidth]{fig/nvt.pressure.1/pressure-l1.eps} %
% \includegraphics[width=0.24\textwidth]{fig/nvt.pressure.1/pressure-l2.eps}%
% \newline
% \includegraphics[width=0.24\textwidth]{fig/nvt.pressure.1/pressure-l3.eps} %
% \includegraphics[width=0.24\textwidth]{fig/nvt.pressure.1/pressure-l4.eps}
\caption{
The pressure convergence with respect to the cut-off radius for ZM
method $l=1$ with splitting parameter from $0.0$ to $2.0\,\text{nm}^{-1}$. The black
solid line indicates the magnitude of the correct pressure: 1~Bar. The error
bars present the statistical uncertainty at 95\% confidence level.}
\label{fig:pres-l1}
\end{figure}

The effect of $\alpha $ in the case of $l=1$ is shown in Fig.~\ref%
{fig:pres-l1}. The result of $\alpha =0.5\,$nm$^{-1}$ is similar to $\alpha
=0$ and shows good convergence. However, a higher $\alpha $ shifts the
pressure to higher side, and in particular $\alpha =2.0\,\text{nm}^{-1}$ is
too large to show no convergence to 1~Bar. This implies that $\alpha \leq 1$
should be used in the simulations where the high accuracy in the pressure is
important. This "anti-damping effect" is similarly seen in the energy
accuracy in the TIP3P model~\cite{fukuda2014zero}.
% [JCP2014 (J. Chem. Phys. 140, 194307 (2014))].
In SI the results of the higher order are shown, which are similar to that
of $l=1$, but indicate less significant dependency on $\alpha $ for a large $%
l$\ and for a small $r_{\text{c}}$, which is consistent with the property of
the pair potential of the ZM~\cite{fukuda2014zero}. The convergence is not sensitive to $%
\alpha $ up to $1.0\,\text{nm}^{-1}$.

\recheck{It should be noted that even with the system $L_0$ that contains 13824 water molecules}, the
fluctuation (measured by standard deviation) of the pressure is roughly
100~Bar, which means that it is very difficult to achieve very accurate
estimate for this quantity. In practice a pressure error of 20~Bar is still
acceptable.

% \begin{table}
%   \centering
%   \caption{A list of the dielectric constant calculated for different systems by different methods.
%     The parameters are provided. The parenthesises in the last column show the statistical uncertainty
%     of the last two digits up to the confidence level of 95~\%.}
%   \begin{tabular*}{0.5\textwidth}{@{\extracolsep{\fill}}cccc rr}\hline\hline
%     System & Method      &       $\alpha$ [$\textrm{nm}^{-1}$] & $r_c$ [nm] &    $l$     &       $\eps$ \\\hline
%     $\systemmb$  &       ZM          &       0.00    &       1.2     &       1       &       99.8 (3.8)\\ 
%     $\systemmb$  &       ZM          &       0.00    &       1.2     &       2       &       95.2 (3.6)\\ 
%     $\systemmb$  &       ZM          &       0.00    &       1.2     &       3       &       93.9 (3.7)\\ 
%     $\systemmb$  &       ZM          &       0.00    &       1.5     &       3       &       98.7 (3.8)\\ 
%     $\systemmb$  &       ZM          &       0.00    &       1.8     &       3       &      100.7 (3.6)\\ 
%     $\systemmb$  &       ZM          &       0.00    &       1.2     &       4       &       94.7 (3.6)\\
%     $\systemmb$   & SPME          & 2.09  & 1.9   &       --      &       98.8 (4.0) \\
%     $\systemmb$  & RF             & --  & 1.2 & -- & 60.6   (1.7) \\
%     $\systemlb$  &       ZM          &       0.00    &       1.2     &       1       &       97.1 (3.2)\\ 
%     $\systemlb$  &       ZM          &       0.00    &       1.2     &       2       &       95.6 (3.5)\\ 
%     $\systemlb$  &       ZM          &       0.00    &       1.2     &       3       &       95.8 (4.6)\\ 
%     $\systemlb$  &       ZM          &       0.00    &       1.5     &       3       &       98.0 (3.3)\\ 
%     $\systemlb$  &       ZM          &       0.00    &       1.8     &       3       &       98.9 (4.2)\\ 
%     $\systemlb$  &       ZM          &       0.00    &       2.1     &       3       &       98.8 (3.9)\\ 
%     $\systemlb$  &       ZM          &       0.00    &       1.2     &       4       &       97.8 (3.9)\\
%    $\systemlb$   & SPME          & 2.09  & 1.9   &       --      &       98.7 (3.5) \\
%     $\systemlb$  & RF             & --  & 1.2 & -- & 60.8   (2.0) \\
%     \hline\hline
%   \end{tabular*}
%   \label{tab:tmp2}
% \end{table}

\subsection{Dielectric quantities}

\begin{figure}[tbp]
\centering
\includegraphics[width=0.5\textwidth]{fig/result.nvt.tiny/fig-eps-t-3000.eps}
\caption{The dielectric constant convergence with respect to
  length of the trajectories used to compute the value.
  The SPME, ZM method $l=1$ to 4 and RF are presented.
  The cut-off distance of ZM and RF methods was 1.2~nm. The working parameters of SPME are given in Sec.~\ref{sec:protocols}
  The system used for simulation is $S_1$.
}
\label{fig:eps-conv}
\end{figure}

The dielectric constant computed by ZM method at different orders are listed
in Tab.~\ref{tab:thermo}, and are consistent with the SPME computed results.
In contrast, the RF method has poor accuracy in the dielectric constant.
It is
well known that the dielectric feature shows system-size dependence~\cite%
{vanderSpoel2006origin}, therefore we further investigated this dependence
and also the effect of the cutoff length, as shown in Table~I of SI. ZM shows
good results without any \recheck{system-size dependency} and indicate $r_{\text{c}}\sim
1.2\, $nm\ being suffice for the accuracy. Since a slow convergence is also known for
the dielectric constant, we have monitored the behavior as shown in Fig.~\ref{fig:eps-conv},
and confirm the sufficient convergence w.r.t.~the length of the trajectories.
\recheck{[COMMENT: the system size and cut-off dependency
  are important,
  but since the result are consistent with system $S_1$ and rc=1.2~nm (shown in table II),
  and NO new phenomenum is observed, 
  they are put in SI.]}

\begin{figure}[tbp]
\centering
\includegraphics[]{fig/result.nvt.small/fig-gkr-small.eps}\\
\includegraphics[]{fig/result.nvt/fig-gkr.eps} 
\caption{The Kirkwood G-factor calculated for system $%
M_{1}$ (a) and $L_{1} $ (b). ZM method of orders $l=1,2,3$ and 4 with the
cut-off 1.2~nm and splitting parameter $\protect\alpha =0.0\,\text{nm}^{-1}$
are plotted. The RF method is shown as an comparison, which uses a cut-off
radius of 1.2~nm and dielectric constant of 80. The statistical uncertainty
of the SPME method is presented at 95~\% confidence level with the red error
bars. the statistical uncertainty of the SPME method is denoted by the red
error bars. The statistical uncertainties of the other methods are
essentially of the same size as the SPME, so they are not presented in the
figure for clarity.}
\label{fig:gkr}
\end{figure}

As a measurement of the dipole correlation as a function of molecular
distance, the Kirkwood-G factor is an important quantity of the water
system. Considering the system size dependence~\cite{vanderSpoel2006origin},
we show the G-factor for system $M_{1}$ in Fig.~\ref{fig:gkr}~(a) and a
larger system $L_{1}$ in Fig.~\ref{fig:gkr} (b). In both the system, the RF
method is qualitatively wrong, and the accuracy of the ZM method is much
higher. In the system of smaller size ($M_{1}$), ZM method of all orders are
highly consistent with the SPME result, and $l=2$ seems the best. In the
system of larger size ($L_{1}$), the accuracies of the ZM method is less for
order $l\geq 2$, while they may be in still acceptable accuracy. In both
systems, ZM $l=1$ presents an artificial oscillation around the cut-off
radius (1.2~nm), while this oscillation is not obvious for $l\geq 2$.

\begin{figure}[tbp]
\centering
\includegraphics[]{fig/result.nvt/fig-gkr-conv.eps} %
\caption{ The cut-off dependency in calculating the Kirkwood-G factor. The
order of ZM method is $l=3$. The splitting parameter is $\protect%
\alpha =0.0\,\text{nm}^{-1}$. The
statistical uncertainty is presented at 95~\% confidence level by the
error bars. }
\label{fig:gkr-conv}
\end{figure}

\begin{figure}[tbp]
\centering
\includegraphics[]{fig/result.nvt/fig-gkr-l1-damp.eps} %
\caption{ The splitting parameter dependency in calculating the Kirkwood-G factor at order $l=1$.
  The cut-off radius is 1.2~nm. The
statistical uncertainty is presented at 95~\% confidence level by the
error bars. }
\label{fig:gkr-damp-l1}
\end{figure}

We thus investigated the cut-off dependency in calculating the Kirkwood-G
factor and present it in Fig.~\ref{fig:gkr-conv} for ZM method of order $l=3$.
Without surprising, the Kirkwood-G factor converges to the SPME result
when using increasingly large cut-off radius.
\recheck{In Fig.~\ref{fig:gkr-damp-l1}, it shows that in the case of $l=1$, 
  the largest splitting parameter ($\alpha=2.0\ \textrm{nm}^{-1}$) is worse in calculating
  the Kirkwood-G factor than smaller splitting parameters.}
Splitting parameter dependency
was not so clear for $l=2$ and 3 (shown in SI).  Note that in many cases the discrepancies
from the SPME were relatively prominent in the middle range of the distance
and they tend small for larger distance.

\subsection{Dynamical quantities}

The dynamical quantities, diffusion constant and viscosity, are listed in
Tab.~\ref{tab:thermo}. The ZM method of order $l\geq 2$ can almost perfectly
reproduce the SPME dynamical quantities. The ZM order $l=1$ is of less
accurate than higher orders, but is more accurate than the RF. Using larger
splitting parameters improves the accuracy of the order $l=1$, as understood
as the damping effect.

\begin{figure}[tbp]
\centering
\includegraphics[]{fig/result.nvt.tiny/fig-vis.eps}
\caption{The convergence
  of the integrated auto-correlation function $I_{\protect\eta }(T)$.
  Different orders of ZM method are compared with the SPME as well as RF results.
  The error bars indicating 95\% confidence level are plotted with the SPME
  method. }
\label{fig:conv-vis}
\end{figure}

\begin{figure}[tbp]
\centering
\includegraphics[]{fig/result.nvt.tiny/fig-vis-l1-damp.eps}
\caption{The convergence
  of the integrated auto-correlation function $I_{\protect\eta }(T)$.
  Different splitting parameters for ZM order $l=1$ are plotted.
The
error bars indicating 95\% confidence level are plotted with the SPME
method. }
\label{fig:conv-vis-damp}
\end{figure}

Similar tendency is confirmed in the auto-correlation function $I_{\eta }(T)$
as shown in Fig.~\ref{fig:conv-vis}. It is clear that the integral for the
RF method converges at 6~ps, while the ZM method converges only in 2~ps,
which is consistent with the SPME result. The value of ZM $l=1$ method is
different from the rest ZM methods and SPME result, but the results was
improved by the damping effect as shown in Fig.~\ref{fig:conv-vis-damp}.

\subsection{Structure property}

\begin{figure}[tbp]
\centering
\includegraphics[]{fig/result.nvt/fig-rdf.eps}
\caption{The comparison of the center-of-mass radial distribution functions
calculated by SPME, ZM and RF methods. The insert is a zoom-in of range 0.9
-- 1.5~nm. In the inset, the position of the cut-off (1.2~nm) is indicated
by a vertical black line. For ZM method, the splitting parameter $\protect%
\alpha $ was set to 0.0~$\text{nm}^{-1}$. }
\label{fig:rdf}
\end{figure}

>>>>

\documentclass[aip,jcp,a4paper,reprint,unsortedaddress,onecolumn,fleqn]{revtex4}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{amsmath,amssymb,amsfonts,latexsym}
\usepackage[dvips]{graphicx}
\usepackage{color}
\usepackage{indentfirst}
\usepackage{rotating,booktabs}

@@

\title{\textbf{Supplementary Materials}\\
  A Critical Appraisal of the Zero-Multiple Method: Structural,
Thermodynamic, Dielectric, and Dynamical Properties of a Water System}
\author{Han Wang}
\email{han.wang@fu-berlin.de}
\author{Ikuo Fukuda}
\email{ifukuda@protein.osaka-u.ac.jp}

@@

\begin{figure}[]
\centering
\includegraphics[width=0.5\textwidth]{fig/nvt.pressure.1/pressure-l2.eps}\\
\includegraphics[width=0.5\textwidth]{fig/nvt.pressure.1/pressure-l3.eps}\\
\includegraphics[width=0.5\textwidth]{fig/nvt.pressure.1/pressure-l4.eps}
\caption{The pressure convergence with respect to the cut-off radius for ZM
methods with splitting parameter from $0.0$ to $2.0\,\text{nm}^{-1}$. From
left to right, the ZM method of order 2 to 4. The black
solid line indicates the magnitude of the correct pressure: 1~Bar. The error
bars present the statistical uncertainty at 95\% confidence level.}
\label{fig:pres-l1}
\end{figure}

\begin{table}
  \centering
  \caption{A list of the dielectric constant calculated for different systems by different methods.
    The parameters are provided. The parenthesises in the last column show the statistical uncertainty
    of the last two digits up to the confidence level of 95~\%.}
  \begin{tabular*}{0.8\textwidth}{@{\extracolsep{\fill}}cccc rr}\hline\hline
    System & Method      &       $\alpha$ [$\textrm{nm}^{-1}$] & $r_c$ [nm] &    $l$     &       $\eps$ \\\hline
    $\systemmb$  &       ZM          &       0.0    &       1.2     &       1       &       99.8 (3.8)\\ 
    $\systemmb$  &       ZM          &       0.0    &       1.2     &       2       &       95.2 (3.6)\\ 
    $\systemmb$  &       ZM          &       0.0    &       1.2     &       3       &       93.9 (3.7)\\ 
    $\systemmb$  &       ZM          &       0.0    &       1.5     &       3       &       98.7 (3.8)\\ 
    $\systemmb$  &       ZM          &       0.0    &       1.8     &       3       &      100.7 (3.6)\\ 
    $\systemmb$  &       ZM          &       0.0    &       1.2     &       4       &       94.7 (3.6)\\
    $\systemmb$   & SPME          & 2.1  & 1.9   &       --      &       98.8 (4.0) \\
    $\systemmb$  & RF             & --  & 1.2 & -- & 60.6   (1.7) \\\hline
    $\systemlb$  &       ZM          &       0.0    &       1.2     &       1       &       97.1 (3.2)\\ 
    $\systemlb$  &       ZM          &       0.0    &       1.2     &       2       &       95.6 (3.5)\\ 
    $\systemlb$  &       ZM          &       0.0    &       1.2     &       3       &       95.8 (4.6)\\ 
    $\systemlb$  &       ZM          &       0.0    &       1.5     &       3       &       98.0 (3.3)\\ 
    $\systemlb$  &       ZM          &       0.0    &       1.8     &       3       &       98.9 (4.2)\\ 
    $\systemlb$  &       ZM          &       0.0    &       2.1     &       3       &       98.8 (3.9)\\ 
    $\systemlb$  &       ZM          &       0.0    &       1.2     &       4       &       97.8 (3.9)\\
   $\systemlb$   & SPME          & 2.1  & 1.9   &       --      &       98.7 (3.5) \\
    $\systemlb$  & RF             & --  & 1.2 & -- & 60.8   (2.0) \\
    \hline\hline
  \end{tabular*}
  \label{tab:tmp2}
\end{table}

\begin{figure}[tbp]
\centering
\includegraphics[]{fig/result.nvt/fig-gkr-l2-damp.eps}\\
\includegraphics[]{fig/result.nvt/fig-gkr-l3-damp.eps}
\caption{  The 
  splitting parameter dependency in calculating the Kirkwood-G factor.
  The orders of ZM method $l=2$ (a)  and $l=3$ (b) are presented.
  In both plots the cut-off radius is 1.2~nm. The
  statistical uncertainty is presented at 95~\% confidence level with the
  error bars. }
\label{fig:gkr-conv-alpha}
\end{figure}

\begin{figure}[tbp]
\centering
\includegraphics[]{fig/result.nvt/fig-rdf-l2-damp.eps}\\
\includegraphics[]{fig/result.nvt/fig-rdf-l3-damp.eps}
\caption{  The 
  splitting parameter dependency in calculating the RDF.
  The orders of ZM method  $l=2$ (b)  and $l=3$ (c) are presented.
  In both plots the cut-off radius is 1.2~nm. }
\label{fig:gkr-conv-alpha}
\end{figure}
